---
title: "ESM 206 Lab 10"
author: "Sarah Hamilton"
date: "11/30/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(usethis)
library(janitor)

#New packages
library(beepr)
library(praise)
library(cowsay)
library(paletteer)
library(sf)
```

## beepr beeps

Use the function `beep()` in the beepr package to make an audio alert when your code is done running.
Use numbers 1-12 ish in the parenthesis.

```{r, eval = FALSE}
for (i in rev(seq(1:9999))) {
  print(paste(i, "bottles of beer on the wall"))
}

beep(4)
```

## praise and cowsay

packages built with a single purpose: to be kind and fun.

```{r}
praise("${Exclamation}, ${EXCLAMATION}...${exclamation}!!!")

praise("Holy ${creating}, Batman - this code is ${ADJECTIVE}")

```

Use cowsay::say() to make a character say somethingn to you.

edit your r profile by typing usethis::edit_r_profile()
and edit the document 

type 
  usethis::use_git()
then answer the two questions
then type
  usethis::use_github()
in the console to make a github repo with existing things


## paletteer to access thousands of color palettes

```{r}
storms %>%
  group_by(name) %>%
  summarize(min_pressure = min(pressure, na.rm = TRUE)) %>%
  slice_min(n = 10, min_pressure) %>%
  ggplot(aes(x = min_pressure, y = name)) +
  geom_col(aes(fill = name)) +
  scale_fill_paletteer_d("tidyquant::tq_green")
```

type
paletteer_d("package_name::pallete_name")
in the console to get a full list of the hex values from the palette

## One spatial data example

```{r}
vegetation <- read_sf("doc.kml") %>%
  select(Name) %>%
  clean_names()

ggplot(data = vegetation) +
  geom_sf(aes(fill = name), color = NA) +
  theme_minimal() +
  scale_fill_paletteer_d("ggthemes::manyeys") +
  labs(title = "Jornada Basin LTER Vegetation",
       caption = "Source: Jornada LTER")
  

```

Create an image of the graph

```{r}
ggsave(filename = "my_awesome_map.jpg", width = 8, height = 5)
```


